### 2017-01-24 local-capability-machine.tex
more added to awkward proof

\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{thmtools}
\usepackage{stmaryrd}
\usepackage{natbib}
\usepackage{url}
\usepackage{array}
\usepackage{arydshln}
\usepackage{ifthen}
\usepackage{ifpdf}
\usepackage{verbatim}
\usepackage{mathpartir}
\usepackage{listings}
\usepackage{hyperref}
\lstset{
  basicstyle=\ttfamily,
  columns=fullflexible,
  keepspaces=true,
  mathescape
}

@@

% Variables
\newcommand{\var}[1]{\mathit{#1}}
\newcommand{\hs}{\var{ms}}
\newcommand{\ms}{\hs}
\newcommand{\hv}{\var{hv}}
\newcommand{\rv}{\var{rv}}
\newcommand{\lv}{\var{lv}}
\newcommand{\gl}{\var{g}}
\newcommand{\pc}{\mathit{pc}}
\newcommand{\pcreg}{\mathrm{pc}}
\newcommand{\addr}{\var{a}}
\newcommand{\offset}{\var{offset}}
\newcommand{\word}{\var{w}}
\newcommand{\start}{\var{base}}
\newcommand{\addrend}{\var{end}}
\newcommand{\pwlv}{\var{pwl}}
\newcommand{\mem}{\var{mem}}
\newcommand{\reg}{\var{reg}}
\newcommand{\heapseg}{\var{ms}}
\newcommand{\heap}{\var{mem}}
\newcommand{\mode}{\var{mode}}
\newcommand{\perm}{\var{perm}}
\newcommand{\permp}{\var{permPair}}
\newcommand{\roll}{\var{roll}}
\newcommand{\instr}{\var{instr}}
\newcommand{\stdcap}[1][(\perm,\gl)]{\left(#1,\start,\addrend,\addr \right)}
\newcommand{\adv}{\var{adv}}
\newcommand{\msframe}{ms_\var{frame}}
\newcommand{\link}{\var{link}}
\newcommand{\stk}{\var{stk}}
\newcommand{\flag}{\var{flag}}
\newcommand{\nwl}{\var{nwl}}
\newcommand{\pwl}{\var{pwl}}
\newcommand{\sta}{\var{sta}}
\newcommand{\cnst}{\var{cnst}}
\newcommand{\olf}{\var{offsetLinkFlag}}
\newcommand{\prp}{\var{prp}}
\newcommand{\env}{\var{env}}
\newcommand{\cls}{\var{cls}}
\newcommand{\unused}{\var{unused}}

@@

\begin{document}
\begin{flushright}
  \today
\end{flushright}

\tableofcontents

\section{Domains and Notation}

@@

              \begin{lemma}[Correctness lemma for \texttt{f1}] \forcenewline
                \label{lem:correctness-f1}
                  c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+\olf) \\
                  c_{f1} & \defeq ((\rwx,\glob),\mathtt{f1}-\olf,\mathtt{1f},\mathtt{f1}) \\
                  m & \defeq \hs_{f1} \uplus 
                      \ms_{\malloc} \uplus 
                      \hs_{\var{frame}} 
                  &\dom(\hs_{f1}) = [\mathtt{f1}-\olf,\mathtt{1f}] \\
                  &\dom(\ms_\link) = [\link,\link+1]\\
                \item $\ms_{f1}(\mathtt{f1}-\olf) = ((\readonly,\glob),\link,\link+1,\link)$, $\ms_{f1}(\mathtt{f1}-\olf+1) = ((\readwrite,\glob),\flag,\flag,\flag)$, the rest of $\hs_{f1}$ contains the code of $f1$.
                \item $\ms_{\var{link}} = [\var{link} \mapsto c_\malloc, \var{link} + 1 \mapsto c_\adv]$
                \item $\hs_\adv$ contains a global read-only capability for $\hs_\link$ on its first address. The remaining cells of the memory segment only contain instructions.
                  (\reg_0\update{\pcreg}{c_{f1}},m) \step[n] (\halted,m'),

@@

                  Use Lemma~\ref{lem:anti-red-obs}, let $\ms_f''$ be given and take $\ms_r$ to be the part of $\ms_3^t$ that $\reg_3(r_\stk)$ does not govern. By the operational semantics, we know\footnote{the execution may fail, but then the confifuration is trivially in the observation relation.}
                  \[
                    (reg_3\update{\pcreg}{\updatePcPerm{c_\cls}},\ms_3^p \uplus \ms_3^t \uplus \ms_f'') \step[j] (\reg_4,\ms_4 \uplus \ms_3^t \uplus \ms_f'')
                  \]
                  where
                  \begin{itemize}
                  \item \lookingat{(reg_4,\ms_4)}{\scall{r_1}{}{r_0,r_1,r_\env}}{c_{\var{next}}}
                    \begin{itemize}
                    \item $c_{\var{next}}$ is the capability pointing to the next instruction.
                    \end{itemize}
                  \item \pointstostack{\reg_4}{\emptyset}{\ms_{\var{unused}}}
                    \begin{itemize}
                    \item \texttt{prepstack} did not fail, so the capability must be $\rwlx$ and follow the stack convention.
                    \end{itemize}
                  \item $\reg_3(r_1)$ is a $\glob$ capability.
                    \begin{itemize}
                    \item \texttt{reqglob} did not fail
                    \end{itemize}
                  \item $\ms_4(x) = 0$
                  \item $\reg_3(r_\env) = c_\env$
                  \end{itemize}
                  region $i_2$ (the $\iota_x$ region) can be in either state $0$ or $1$, so to make sure it is in state $0$, we use a private transition. So let $W_4$ be $\revokeTemp{W_3}$ with region $i_2$ in state $0$. We then have
                  \[
                    \memSat[n_4-j]{\ms_4}{W_4}
                  \]
                  Now we can use Lemma~\ref{lem:scall-works} to show:
                  \[
                    \npair[n_4-j]{(\reg_4,\ms_4 \uplus \ms_3^t)} \in \observations(W_4)
                  \]
                  \begin{enumproof}
                    \item $\memSat[n_4-j]{\ms_4}{\revokeTemp{W_4}}$: follows from $W_4 = \revokeTemp{W_4}$
                    \item Hyp-Callee\\
                      We know $\npair[n_4]{\reg_3(r_1)} \in \stdvr(W_3)$. If this is not a capability that becomes executable when jumped to, then the execution fails, so the register memory segment pair is trivially in the observation relation. If it is executable, then either the $\execCond{}$ or the $\entryCond{}$ holds for appropriate values. We also know that it is a global capability, so we can use it with private future worlds. We have $W_5 = \revokeTemp{W_4}[\iota^\sta (\temp,\emptyset)][\iota^\pwl(\dom(\ms_\unused))] \futurestr W_3$, so by the conditions, we have
                      \[
                        \npair[n_4-j]{\updatePcPerm{reg_3(r_1)}} \in \observations(W_5)
                      \]
                      Now it suffices to show
                      \begin{enumproof}
                        \item $\memSat[n_4-j-1]{\ms_5}{W_5}$ for some $\ms_5$ which is one of the assumptions of Hyp-Callee.
                        \item $\npair[n_4-j-1]{\reg_5} \in \stdrr(W_5)$ where $\reg_5$ is as described in the \texttt{scall} lemma Hyp-callee premise.\\
                          Amounts to showing:\lau{too deply nested for environments}\\
                          1) $\npair[n_4-j-1]{\reg_3(r_1)} \in \stdvr(W_5)$, use Lemma~\ref{lem:stdvr-glob-priv-mono} with $\npair[n_4-j-1]{\reg_3(r_1)} \in \stdvr(W_3)$, the capability is global, and $W_5 \futurestr W_3$.

                          2) The protected return pointer is in the value relation by Hyp-callee assumption, and the stack capability is handled by lemma~\ref{lem:stack-cap-vr}.
                      \end{enumproof}
                      which gives us
                      \[
                        \npair[n_4-j-1]{(\reg_5,\ms_5)} \in \observations(W_5)
                      \]
                    \item Hyp-Cont\\
                      Assume
                      \begin{itemize}
                      \item $n_5 \leq n_4-j-2$
                      \item $W_6 \futurewk W_5$ (as defined in the Hyp-Callee case).
                      \item $\memSat[n_4]{\ms_6}{\revokeTemp{W_6}}$
                      \item $\reg_6(\pcreg) = c_{\var{next}}$, $\reg_6(r_0) = \reg_3(r_0)$, $\reg_6(r_1) = \reg_3(r_1)$, $\reg(r_\env) = c_\env$
                      \item \pointstostack{\reg_6}{\emptyset}{\ms_\unused'}
                      \end{itemize}
                      Use the $\observations$-anti-reduction lemma (Lemma~\ref{lem:anti-red-obs}) followed by the \texttt{scall} lemma (Lemma~\ref{lem:scall-works}). Given $\ms_f'''$, we know by the operational semantics and the fact that the program hasn't changed that
                      \[
                        (\reg_6,\ms_6 \uplus \ms_\unused''' \uplus \ms_f''') \step[k] (\reg_7,\ms_6\update{x}{1} \uplus \ms_\unused'' \uplus \ms_f''')
                      \]
                      where
                      \begin{itemize}
                      \item \lookingat{(\reg_7,\ms_6\update{x}{1})}{\mathtt{scall}\;r([],[r_0,r_\env])}{c_{\var{next}}'}\\
                        $c_{\var{next}}'$ is the current $\pcreg$ capability but looking at \texttt{load} $r_1$ $x$.
                      \item $\reg_7(r_0,r_1,r_\env,r_\stk) = \reg_6(r_0,r_1,r_\env,r_\stk)$
                      \end{itemize}
                      In $\revokeTemp{W_6}$, we don't know which state the $\iota_x$ region is in, but state $1$ is reachable via a public transition, so let $W_7$ be $\revokeTemp{W_6}$ with region $i_2$ in state $1$. It follows easily that
                      \[
                        \memSat[n_4-k]{\ms_6\update{x}{1}}{W_7}
                      \]
                      We continue the proof in item \ref{item:proof-cont}
                  \end{enumproof}
              \end{enumproof}
          \end{enumproof}
      \end{enumproof}
      \item \label{item:proof-cont} At this point, we apply the \texttt{scall} lemma, to get
        \[
          \npair[n_4-k]{(\reg_7,\ms_6\update{x}{1} \uplus \ms_\unused'')} \in \observations(W_7)
        \]
        show
        \begin{enumproof}
          \item $\memSat[n_4-k]{\ms_6\update{x}{1}}{\revokeTemp{W_7}}$, follows from $W_7= \revokeTemp{W_7}$.
          \item Hyp-Callee
            % Use that it is the same $r_1$
            % TODO
          \item Hyp-Cont
            % From c_stk in val rel of W_3 get that W_3 must have iota pwl region.
            % 
        \end{enumproof}
  \end{enumproof}

@@

Define the function $\activeReg{\cdot}$ as follows
\begin{align*}
  \activeReg{} & : \Worlds \fun 2^\RegionNames \\
  \activeReg{W} & \defeq \dom(\erase{W}{\perma,\temp})
\end{align*}

@@

Standard regions for when writing locally is permitted:
\begin{align*}
  &\iota_{\start,\addrend}^\pwl : \Regions\\
  &\iota_{\start,\addrend}^\pwl \defeq (\temp,1,=,=,H^\pwl_{\start,\addrend}) \\
  \\
  &H^\pwl : \Addrs^2 \fun \States \fun (\Wor \monwknefun \UPred{\HeapSegments})\\
  &H^\pwl_{\start,\addrend}\; s \; \hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \npair[n-1]{\hs(\addr)} \in \stdvr(\xi(\hat{W}))
    \end{aligned}
        \right\}
\end{align*}
\lau{What is the reason to have the ``view'' always be $\temp$? It seems like it does not play well with the read condition if it is always $\temp$.}
\dominique{The comment immediately above is outdated, right?}
Revoking all temporary regions:
\begin{align*}
  \revokeTemp{} & : \Worlds \fun \Worlds \\
  \revokeTemp{W} & \defeq \lambda r \ldotp 
                   \begin{cases}
                     (\revoked,s,\phi_\pub,\phi,H)            & \text{if }W(r) = (\temp,s,\phi_\pub,\phi,H) \\
                     W(r)                & \text{otherwise}
                   \end{cases}
\end{align*}
\newcommand{\wrev}[1]{\revokeTemp{#1}}

@@

\begin{lemma}[$\mathtt{scall}$ works]
  \label{lem:scall-works}
  If
  \begin{itemize}
  \item $\memSat[n]{\ms}{\revokeTemp{W}}$ 
  \item $\dom(\ms_f) \cup (\dom(\ms_\stk \uplus \ms_{\mathit{unused}} \uplus \ms)) = \emptyset$
  \item $(\reg,\ms) \text{ is looking at }
    \mathtt{scall}(r(\overline{r_{\mathit{arg}}},
    \overline{r_{\mathit{priv}}})) \text{ followed by } c_{\mathit{next}}$
  \item $\reg \text{ points to stack with $\ms_\stk$ used and $\ms_{\mathit{unused}}$ unused}$
  \item[Hyp-Callee] If
    \begin{itemize}
    \item $\dom(\ms_{\mathit{unused}}) = \dom(\ms_{\mathit{act}}
      \uplus \ms_{\mathit{unused}}')$,
    \item $W' =
      \revokeTemp{W}[\iota^{\sta}(\temp,\ms_\stk\uplus\ms_{\mathit{act}}),\iota^{\pwl}(\dom(\ms_{\mathit{unused}}')),\iota^\sta (\temp,\ms_f)]$,
    \item $\memSat[n-1]{\ms''}{W'}$
    \item $\reg' \text{ points to stack with $\emptyset$ used and $\ms_{\mathit{unused}'}$ unused}$
    \item $\forall a \in \dom(\ms_{\var{unused}}') \ldotp \ms''(a) = 0$
    \item $\reg'= \reg_0[\pcreg\mapsto\updatePcPerm{\reg(r)},
      \overline{r_{\mathit{arg}}} \mapsto \reg(\overline{r_{\mathit{arg}}}),r_0
      \mapsto c_{\mathit{ret}}, r_\stk \mapsto \_, r \mapsto \reg(r)]$ 
    \item $(n,c_{\mathit{ret}}) \in \stdvr(W')$
    \end{itemize}

    then we have that $(n-1,(\reg',\ms'')) \in \observations(W')$
  \item[Hyp-Cont] If
    \begin{itemize}
    \item $n' \leq n-2$
    \item $W'' \futurewk \revokeTemp{W}[\iota^{\sta}(\temp,\ms_\stk)][\iota^\sta(\temp,\ms_{\mathit{unused}}'')][\iota^\sta(\temp,\ms_f)]$
    \item $\memSat[n']{\ms''}{\revokeTemp{W''}}$ 
    \item for all $r$, we have that:
      \begin{equation*}
        \reg'(r)
        \begin{cases}
          = c_{\mathit{next}} &\text{ if } r = \pcreg\\
          = \reg(r)&\text{ if } r \in \overline{r_{\mathit{priv}}}\\
          \in \stdvr(W'') &\text{ if $\reg'(r)$ is a global capability and } r \not\in \{\pcreg,\overline{r_{\mathit{priv}}}, r_\stk\} %revokeTemp here?
        \end{cases}
      \end{equation*}
    \item $\reg' \text{ points to stack with $\ms_\stk$ used and $\ms_{\mathit{unused}}''$ unused}$ for some $\ms_{\mathit{unused}}''$
    \end{itemize}

>>>>

\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{thmtools}
\usepackage{stmaryrd}
\usepackage{natbib}
\usepackage{url}
\usepackage{array}
\usepackage{arydshln}
\usepackage{ifthen}
\usepackage{ifpdf}
\usepackage{verbatim}
\usepackage{mathpartir}
\usepackage{listings}
\lstset{
  basicstyle=\ttfamily,
  columns=fullflexible,
  keepspaces=true,
  mathescape
}

@@

% Variables
\newcommand{\var}[1]{\mathit{#1}}
\newcommand{\hs}{\var{ms}}
\newcommand{\ms}{\hs}
\newcommand{\hv}{\var{hv}}
\newcommand{\rv}{\var{rv}}
\newcommand{\lv}{\var{lv}}
\newcommand{\gl}{\var{g}}
\newcommand{\pc}{\mathit{pc}}
\newcommand{\pcreg}{\mathrm{pc}}
\newcommand{\addr}{\var{a}}
\newcommand{\offset}{\var{offset}}
\newcommand{\word}{\var{w}}
\newcommand{\start}{\var{base}}
\newcommand{\addrend}{\var{end}}
\newcommand{\pwlv}{\var{pwl}}
\newcommand{\mem}{\var{mem}}
\newcommand{\reg}{\var{reg}}
\newcommand{\heapseg}{\var{ms}}
\newcommand{\heap}{\var{mem}}
\newcommand{\mode}{\var{mode}}
\newcommand{\perm}{\var{perm}}
\newcommand{\permp}{\var{permPair}}
\newcommand{\roll}{\var{roll}}
\newcommand{\instr}{\var{instr}}
\newcommand{\stdcap}[1][(\perm,\gl)]{\left(#1,\start,\addrend,\addr \right)}
\newcommand{\adv}{\var{adv}}
\newcommand{\msframe}{ms_\var{frame}}
\newcommand{\link}{\var{link}}
\newcommand{\stk}{\var{stk}}
\newcommand{\flag}{\var{flag}}
\newcommand{\nwl}{\var{nwl}}
\newcommand{\pwl}{\var{pwl}}
\newcommand{\sta}{\var{sta}}
\newcommand{\cnst}{\var{cnst}}
\newcommand{\olf}{\var{offsetLinkFlag}}
\newcommand{\prp}{\var{prp}}
\newcommand{\env}{\var{env}}
\newcommand{\cls}{\var{cls}}
\newcommand{\unused}{\var{unused}}
\newcommand{\act}{\var{act}}

@@

\begin{document}
\begin{flushright}
  \today
\end{flushright}
\section{Domains and Notation}

@@

              \begin{lemma}[Correctness lemma for \texttt{f1}] \forcenewline
                \label{lem:correctness-f1}
                For all $n \in \nats$
                let
                \begin{align*}
                  c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+\olf) \\
                  c_{f1} & \defeq ((\rwx,\glob),\mathtt{f1}-\olf,\mathtt{1f},\mathtt{f1}) \\
                  c_\malloc & \defeq ((\entry,\glob),\start_\malloc,\addrend_\malloc,\start_\malloc+\olf) \\
                  m & \defeq \hs_{f1} \uplus 
                      \hs_\flag \uplus                
                      \ms_{\var{link}} \uplus 
                      \hs_\adv \uplus 
                      \ms_{\malloc} \uplus 
                      \hs_{\var{frame}} 
                \end{align*}
                where 
                \begin{align*}
                  &\dom(\hs_{f1}) = [\mathtt{f1}-\olf,\mathtt{1f}] \\
                  &\dom(\hs_\flag) = [\flag,\flag] \\
                  &\dom(\ms_\link) = [\link,\link+1]\\
                  &\dom(\hs_{\adv}) = [\start_\adv,\addrend_\adv] \\
                  &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc,0}]}
                \end{align*}
                and
                \begin{itemize}
                \item $\ms_{f1}(\mathtt{f1}-\olf) = ((\readonly,\glob),\link,\link+1,\link)$, $\ms_{f1}(\mathtt{f1}-\olf+1) = ((\readwrite,\glob),\flag,\flag,\flag)$, the rest of $\hs_{f1}$ contains the code of $f1$.
                \item $\ms_\flag = [\flag \mapsto 0]$
                \item $\ms_{\var{link}} = [\var{link} \mapsto c_\malloc, \var{link} + 1 \mapsto c_\adv]$
                \item $\hs_\adv$ contains a global read-only capability for $\hs_\link$ on its first address. The remaining cells of the memory segment only contain instructions.
                \end{itemize}
                if 
                \[
                  (\reg_0\update{\pcreg}{c_{f1}},m) \step[n] (\halted,m'),
                \]
                then
                \[
                  m'(\flag) = 0
                \]  
              \end{lemma}

@@

                  Use Lemma~\ref{lem:anti-red-obs}, let $\ms_f''$ be given and take $\ms_r$ to be the part of $\ms_3^t$ that $\reg_3(r_\stk)$ does not govern. By the operational semantics, we know\footnote{the execution may fail, but then the configuration is trivially in the observation relation.}
                  \[
                    (reg_3\update{\pcreg}{\updatePcPerm{c_\cls}},\ms_3^p \uplus \ms_3^t \uplus \ms_f'') \step[j] (\reg_4,\ms_4 \uplus \ms_3^t \uplus \ms_f'')
                  \]
                  where
                  \begin{itemize}
                  \item \lookingat{(reg_4,\ms_4)}{\scall{r_1}{}{r_0,r_1,r_\env}}{c_{\var{next}}}
                    \begin{itemize}
                    \item $c_{\var{next}}$ is the capability pointing to the next instruction.
                    \end{itemize}
                  \item \pointstostack{\reg_4}{\emptyset}{\ms_{\var{unused}}}
                    \begin{itemize}
                    \item \texttt{prepstack} did not fail, so the capability must be $\rwlx$ and follow the stack convention.
                    \end{itemize}
                  \item $\reg_3(r_1)$ is a $\glob$ capability.
                    \begin{itemize}
                    \item \texttt{reqglob} did not fail
                    \end{itemize}
                  \item $\ms_4(x) = 0$
                  \item $\reg_3(r_\env) = c_\env$
                  \end{itemize}
                  region $i_2$ (the $\iota_x$ region) can be in either state $0$ or $1$, so to make sure it is in state $0$, we use a private transition. So let $W_4$ be $\revokeTemp{W_3}$ with region $i_2$ in state $0$. We then have
                  \[
                    \memSat[n_4-j]{\ms_4}{W_4}
                  \]
                  Now we can use Lemma~\ref{lem:scall-works} to show:
                  \[
                    \npair[n_4-j]{(\reg_4,\ms_4 \uplus \ms_r \uplus \emptyset \uplus \ms_\unused)} \in \observations(W_4)
                  \]
                  where $\ms_r$ is the local frame of the \texttt{scall} lemma.
                  \begin{enumproof}
                    \item $\memSat[n_4-j]{\ms_4}{\revokeTemp{W_4}}$: follows from $W_4 = \revokeTemp{W_4}$
                    \item Hyp-Callee\\
                      We know $\npair[n_4]{\reg_3(r_1)} \in \stdvr(W_3)$. If this is not a capability that becomes executable when jumped to, then the execution fails, so the register memory segment pair is trivially in the observation relation. If it is executable, then either the $\execCond{}$ or the $\entryCond{}$ holds for appropriate values. We also know that it is a global capability, so we can use it with private future worlds. We have $W_5 = \revokeTemp{W_4}[\iota^\sta (\temp,\emptyset \uplus \ms_\act),\iota^\pwl(\dom(\ms_\unused')),\iota^\sta(\temp,\ms_f)] \futurestr W_3$, for some $\ms_\act$ and $\ms_\unused'$. By the execute/enter condition, we have
                      \[
                        \npair[n_4-j]{\updatePcPerm{reg_3(r_1)}} \in \stder(W_5)
                      \]
                      Now it suffices to show
                      \begin{enumproof}
                        \item $\memSat[n_4-j-1]{\ms_5}{W_5}$ for some $\ms_5$ which is one of the assumptions of Hyp-Callee.
                        \item $\npair[n_4-j-1]{\reg_5} \in \stdrr(W_5)$ where $\reg_5$ is as described in the \texttt{scall} lemma Hyp-callee premise.\\
                          Amounts to showing:\lau{too deply nested for environments}\\
                          1) $\npair[n_4-j-1]{\reg_3(r_1)} \in \stdvr(W_5)$, use Lemma~\ref{lem:stdvr-glob-priv-mono} with $\npair[n_4-j-1]{\reg_3(r_1)} \in \stdvr(W_3)$, the capability is global, and $W_5 \futurestr W_3$.

                          2) The protected return pointer is in the value relation by Hyp-callee assumption, and the stack capability is handled by lemma~\ref{lem:stack-cap-vr}.
                      which gives us
                        \npair[n_4-j-1]{(\reg_5,\ms_5)} \in \observations(W_5)
                      \item $n_5 \leq n_4-j-2$
                      \item $W_6 \futurewk \revokeTemp{W_4}[\iota^\sta (\temp,\emptyset \uplus \ms_\act),\iota^\pwl(\dom(\ms_\unused'')),\iota^\sta(\temp,\ms_f)]$ 
                      \item $\memSat[n_5]{\ms_6}{\revokeTemp{W_6}}$
                      \item $\reg_6(\pcreg) = c_{\var{next}}$, $\reg_6(r_0) = \reg_3(r_0)$, $\reg_6(r_1) = \reg_3(r_1)$, $\reg(r_\env) = c_\env$
                      \item \pointstostack{\reg_6}{\emptyset}{\ms_\unused''}
                        \npair[n_5]{(\reg_6,\ms_6 \uplus \ms_r \uplus \emptyset \uplus \ms_\unused'')} \in \observations(W_6)
                      Use the $\observations$-anti-reduction lemma (Lemma~\ref{lem:anti-red-obs}) followed by the \texttt{scall} lemma (Lemma~\ref{lem:scall-works}). Given $\ms_f'''$, we know by the operational semantics and the fact that the program hasn't changed that
                        (\reg_6,\ms_6 \uplus \ms_r \uplus \ms_\unused'' \uplus \ms_f''') \step[k] (\reg_7,\ms_6\update{x}{1} \uplus \ms_r \uplus \ms_\unused'' \uplus \ms_f''')
                      \item \lookingat{(\reg_7,\ms_6\update{x}{1})}{\mathtt{scall}\;r([],[r_0,r_\env])}{c_{\var{next}}'}\\
                        $c_{\var{next}}'$ is the current $\pcreg$ capability but looking at \texttt{load} $r_1$ $x$.
                      \item $\reg_7(r_0,r_1,r_\env,r_\stk) = \reg_6(r_0,r_1,r_\env,r_\stk)$
                      In $\revokeTemp{W_6}$, we don't know which state the $\iota_x$ region is in, but state $1$ is reachable via a public transition, so let $W_7$ be $\revokeTemp{W_6}$ with region $i_2$ in state $1$. It follows easily that
                        \memSat[n_5-k]{\ms_6\update{x}{1}}{W_7}
                      We continue the proof in item \ref{item:proof-cont}
      \item \label{item:proof-cont} At this point, we apply the \texttt{scall} lemma, to get
          \npair[n_5-k]{(\reg_7,\ms_6\update{x}{1} \uplus \ms_r \uplus \ms_\unused''')} \in \observations(W_7)
          \item $\memSat[n_5-k]{\ms_6\update{x}{1}}{\revokeTemp{W_7}}$, follows from $W_7= \revokeTemp{W_7}$.
          \item Hyp-Callee
            % Use that it is the same $r_1$
            \item $n_6 \leq n_5-k-2$
            \item $W_8 \futurewk \revokeTemp{W_7}[\iota^{\sta}(\temp,\ms_\act)][\iota^\sta(\temp,\ms_{\mathit{unused}}^{(5)})][\iota^\sta(\temp,\ms_r)]$
            \item $\memSat[n_6]{\ms_7}{\revokeTemp{W_8}}$ 
            \item $\reg_8(r_0,r_\env) = \reg_7(r_0,r_\env)$
            \item $\reg_8(\pcreg) = c_{\var{next}}'$
            \item $\reg_8 \text{ points to stack with $\emptyset$ used and $\ms_{\mathit{unused}}^{(6)}$ unused}$ for some $\ms_{\mathit{unused}}^{(6)}$
            Show:
              \npair[n_6]{(\reg_8,\ms_7 \uplus \ms_r \uplus \emptyset \uplus \ms_\unused^{(5)})} \in \observations(W_8)
            Use Lemma~\ref{lem:anti-red-obs}. Let $\ms_f$ be given, then
              (\reg_8,\ms_7 \uplus \ms_r \uplus \emptyset \uplus \ms_\unused^{(5)}) \step[l] (reg_9,\ms_7 \uplus \ms_r \uplus \emptyset \uplus \ms_0)
            \item $\reg_9(\pcreg) = \updatePcPerm{\reg_3(r_0)}$ (note $\reg_8(r_0) = \reg_3(r_0)$)
            \item $\reg_9(r_0) = reg_3(r_0)$
            \item For all $r \not\in \{\pcreg,r_0\}$, $\reg_9(r) = 0$.
            \item $\dom(\ms_0) = \dom(\ms_\unused^{(5)})$ and $\forall a \in \dom(\ms_0) \ldotp \ms_0(a) = 0$
            The execution proceeds as above because $\iota_x$ in $W_8$ is in state $1$, so $\ms_7(x) = 1$ which causes the assertion to succeed. Subsequently the stack and most of the registers are cleared.

            Now take $W_{10}$ to be $W_9$ with all the regions in $\dom(\erase{W_3}{\temp})$ reinstated. Now we show the following:
            \begin{enumproof}
            \item $W_{10} \futurewk W_3$\\
              We have
              \[
                \forall r \in \dom(W_3) \ldotp W_3 = W_{10}
              \]
              if the region is permanent, then it is there because $W_{10} \futurestr W_3$. If it is temporary, then it is there because it was just reinstated.

              All the future worlds we have been given have been public, so the regions can only have made public transitions. In $W_3$ region $\iota_x$ is in state 0 or 1. In $W_{10}$ region $\iota_x$ is in state 1. State 1 can be reached from 0 and 1 using a public transition, so the $\iota_x$ in $W_{10}$ is a public future region of the $\iota_x$ in $W_3$.

              In other words, all the regions in $W_3$ have only taken public transitions compared to the corresponding regions in $W_{10}$.

            \item $\memSat[n_6-l]{\ms_7 \uplus \ms_r \uplus \emptyset \uplus \ms_0}{W_{10}}$
            \item $\npair[n_6-l]{\reg_9} \in \stdrr(W_{10})$
            \end{enumproof}
            % From c_stk in val rel of W_3 get that W_3 must have iota pwl region.
            % 
        \end{enumproof}
  \end{enumproof}

@@

Define the function $\active{}$ as follows
\begin{align*}
  \activeReg{} & : \Worlds \fun 2^\RegionNames \\
  \activeReg{W} & \defeq \dom(\erase{W}{\perma,\temp})
\end{align*}

@@

Standard regions for when writing locally is permitted:
\begin{align*}
  &\iota_{\start,\addrend}^\pwl : \Regions\\
  &\iota_{\start,\addrend}^\pwl \defeq (\temp,1,=,=,H^\pwl_{\start,\addrend}) \\
  \\
  &H^\pwl : \Addrs^2 \fun \States \fun (\Wor \monwknefun \UPred{\HeapSegments})\\
  &H^\pwl_{\start,\addrend}\; s \; \hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \npair[n-1]{\hs(\addr)} \in \stdvr(\xi(\hat{W}))
    \end{aligned}
        \right\}
\end{align*}
\lau{What is the reason to have the ``view'' always be $\temp$? It seems like it does not play well with the read condition if it is always $\temp$.}
Revoking all temporary regions:
\begin{align*}
  \revokeTemp{} & : \Worlds \fun \Worlds \\
  \revokeTemp{W} & \defeq \lambda r \ldotp 
                   \begin{cases}
                     (\revoked,s,\phi_\pub,\phi,H)            & \text{if }W(r) = (\temp,s,\phi_\pub,\phi,H) \\
                     W(r)                & \text{otherwise}
                   \end{cases}
\end{align*}
\newcommand{\wrev}[1]{\revokeTemp{#1}}

@@

\begin{lemma}[$\mathtt{scall}$ works]
  \label{lem:scall-works}
  If
  \begin{itemize}
  \item $\memSat[n]{\ms}{\revokeTemp{W}}$ 
  \item $\dom(\ms_f) \cap (\dom(\ms_\stk \uplus \ms_{\mathit{unused}} \uplus \ms)) = \emptyset$
  \item $(\reg,\ms) \text{ is looking at }
    \mathtt{scall}(r(\overline{r_{\mathit{arg}}},
    \overline{r_{\mathit{priv}}})) \text{ followed by } c_{\mathit{next}}$
  \item $\reg \text{ points to stack with $\ms_\stk$ used and $\ms_{\mathit{unused}}$ unused}$
  \item[Hyp-Callee] If
    \begin{itemize}
    \item $\dom(\ms_{\mathit{unused}}) = \dom(\ms_{\mathit{act}}
      \uplus \ms_{\mathit{unused}}')$,
    \item $W' =
      \revokeTemp{W}[\iota^{\sta}(\temp,\ms_\stk\uplus\ms_{\mathit{act}}),\iota^{\pwl}(\dom(\ms_{\mathit{unused}}')),\iota^\sta (\temp,\ms_f)]$,
    \item $\memSat[n-1]{\ms''}{W'}$
    \item $\reg' \text{ points to stack with $\emptyset$ used and $\ms_{\mathit{unused}}'$ unused}$
    \item $\forall a \in \dom(\ms_{\var{unused}}') \ldotp \ms''(a) = 0$
    \item $\reg'= \reg_0[\pcreg\mapsto\updatePcPerm{\reg(r)},
      \overline{r_{\mathit{arg}}} \mapsto \reg(\overline{r_{\mathit{arg}}}),r_0
      \mapsto c_{\mathit{ret}}, r_\stk \mapsto \_, r \mapsto \reg(r)]$ 
    \item $(n,c_{\mathit{ret}}) \in \stdvr(W')$
    \end{itemize}

    then we have that $(n-1,(\reg',\ms'')) \in \observations(W')$
  \item[Hyp-Cont] If
    \begin{itemize}
    \item $n' \leq n-2$
    \item $W'' \futurewk \revokeTemp{W}[\iota^{\sta}(\temp,\ms_\stk\uplus \ms_\act)][\iota^\sta(\temp,\ms_{\mathit{unused}}'')][\iota^\sta(\temp,\ms_f)]$
    \item $\memSat[n']{\ms''}{\revokeTemp{W''}}$ 
    \item for all $r$, we have that:
      \begin{equation*}
        \reg'(r)
        \begin{cases}
          = c_{\mathit{next}} &\text{ if } r = \pcreg\\
          = \reg(r)&\text{ if } r \in \overline{r_{\mathit{priv}}}\\
          \in \stdvr(W'') &\text{ if $\reg'(r)$ is a global capability and } r \not\in \{\pcreg,\overline{r_{\mathit{priv}}}, r_\stk\} %revokeTemp here?
        \end{cases}
      \end{equation*}
    \item $\reg' \text{ points to stack with $\ms_\stk$ used and $\ms_{\mathit{unused}}''$ unused}$ for some $\ms_{\mathit{unused}}''$
    \end{itemize}
